Contention management for Cloud RAN over an optical ring

### 2018-02-21 Papier NGreen/article.tex

      \captionof{figure}{Performances of FIFO and C-RAN first.}    \label{fig:resultopport}
      \end{center} 
  \end{minipage}
\hfill
  \begin{minipage}[b]{0.40\linewidth}
  \vspace{-2cm}
  \scalebox{0.7}
  {
  \centering
  \begin{tabular}{|c|c|}
  \hline
 Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Container size  $C$ & $12,500$ B  \tabularnewline
  \hline
  Slot duration $C/F\times R$ & $1\mu$ s \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ \tabularnewline
  \hline
   Period $P$ & $1,000$ \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of nodes $n$ & $5$  \tabularnewline
  \hline
  \end{tabular}
  }
  \vspace{0.75cm}
  \captionof{figure}{Parameters experiments from the N-GREEN architecture}\label{fig:params}

@@

Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
Therefore to not waste bandwith, it is relevant to put as many RRH as possible on the same positions. Moreover unused position in an assignment are useful to guarantee a good latency to BE traffic. The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{}.

However, for some parameters, there is no unused position. In particular, with the current parameters of the N-GREEN ring,
$ET = \frac{P}{2}$, $F = 10$ and $n = 5$. Hence there is a BBU or an RRH at each position. If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for $BE$-traffic. 
To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{}.

We present the cumulative of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
Fig.~\ref{fig:optimres}. Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
% 
% \begin{prop}
%  If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
%  \end{prop}
% %  \begin{proof}
% One show that proposition by induction.
%  In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
%  {\bf Base case:} 
%  Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
%  We assume that $A$ starts to emit a time $1$ during $ET$ slots. The containers of $A$ arrive in $B$ during the interval $[\omega(A,B);\omega(A,B)+ET[$. Then, $B$ can immediately emits its containers at time $\omega(A,B)+ET$. Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;\omega(A,B)+ET + \omega(B,A) + ET ] = [ET+RS;2.ET+RS] = [ET + RS; P]$. Then, $A$ can emit in the next period, without collisions.
% Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
%  
%  {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$. One must show that if there is one more RRH on the ring, the period must be at least $P = (n+1)\times ET + RS$. 
%  
% Take a sequence of container of size $P$ on a ring with $n$ RRH. One can observe that this sequence is the same at every nodes, shifted of the length of the routes between the nodes. For instance, with two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted by $\omega(A,B)$.
% In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH. Thus a period $P = (n+1)\times ET + RS$ is enough to carry the traffic of $n+1$ RRH.
% %  \end{proof}
% 
% For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages. To this end, the pairs must be filled with as much RRH as possible. Then, the free pairs are uniformly apportioned into the macro slot. Nevertheless, this is not always enough to ensure a good BE traffic latency. Indeed, with the previous parameters, with $ET = \frac{P}{2}$, $F = 10$ and $n = 5$, a pair is given to each antenna, and if all the RRH starts to emit in the same macro slots, a long sequence of reserved container will highly impact the latency of the BE traffic. The solution to this issue is to uniformly distribute the BBU-offset of the first RRH of a pair on the period. In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic. Fig.~\ref{fig:optimres} is a compariason between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here. Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
   \begin{figure}[h]
\centering
      \includegraphics[scale=0.3]{optim.pdf}
     \caption{Impact of the reservation of the traffics.}   \label{fig:optimres}
  \end{figure}

  The performance of the reservation algorithm is excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule. It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth to the BE traffic.

>>>>

      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
      \end{center} 
  \end{minipage}
\hfill
  \begin{minipage}[b]{0.40\linewidth}
  \vspace{-2cm}
  \scalebox{0.7}
  {
  \centering
  \begin{tabular}{|c|c|}
  \hline
 Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Container size  $C$ & $12,500$ B  \tabularnewline
  \hline
  Slot duration $C/F\times R$ & $1\mu$ s \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ \tabularnewline
  \hline
   Period $P$ & $1,000$ \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of nodes $n$ & $5$  \tabularnewline
  \hline
   Load induced by C-RAN & $50\%$  \tabularnewline
  \hline
  \end{tabular}
  }
  \vspace{0.55cm}
  \captionof{figure}{Experimental parameters from the N-GREEN architecture}\label{fig:params}

@@

Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
Therefore to not waste bandwidth, it is relevant to put as many RRH as possible on the same positions. Moreover unused position in an assignment are useful to guarantee a good latency to BE traffic. The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{fig:repart1}.

However, it is possible that there are no unused position. It happens with the current parameters of the N-GREEN ring,
$ET = \frac{P}{2}$, $F = 10$ and $n = 5$. Hence there is exactly one  BBU or RRH at each position. If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for $BE$-traffic. 
To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{fig:repart2}.

We present the cumulative of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
Fig.~\ref{fig:optimres}. Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
% 
% \begin{prop}
%  If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
%  \end{prop}
% %  \begin{proof}
% One show that proposition by induction.
%  In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
%  {\bf Base case:} 
%  Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
%  We assume that $A$ starts to emit a time $1$ during $ET$ slots. The containers of $A$ arrive in $B$ during the interval $[\omega(A,B);\omega(A,B)+ET[$. Then, $B$ can immediately emits its containers at time $\omega(A,B)+ET$. Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;\omega(A,B)+ET + \omega(B,A) + ET ] = [ET+RS;2.ET+RS] = [ET + RS; P]$. Then, $A$ can emit in the next period, without collisions.
% Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
%  
%  {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$. One must show that if there is one more RRH on the ring, the period must be at least $P = (n+1)\times ET + RS$. 
%  
% Take a sequence of container of size $P$ on a ring with $n$ RRH. One can observe that this sequence is the same at every nodes, shifted of the length of the routes between the nodes. For instance, with two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted by $\omega(A,B)$.
% In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH. Thus a period $P = (n+1)\times ET + RS$ is enough to carry the traffic of $n+1$ RRH.
% %  \end{proof}
% 
% For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages. To this end, the pairs must be filled with as much RRH as possible. Then, the free pairs are uniformly apportioned into the macro slot. Nevertheless, this is not always enough to ensure a good BE traffic latency. Indeed, with the previous parameters, with $ET = \frac{P}{2}$, $F = 10$ and $n = 5$, a pair is given to each antenna, and if all the RRH starts to emit in the same macro slots, a long sequence of reserved container will highly impact the latency of the BE traffic. The solution to this issue is to uniformly distribute the BBU-offset of the first RRH of a pair on the period. In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic. Fig.~\ref{fig:optimres} is a compariason between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here. Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.

  \begin{minipage}[b]{0.4\linewidth}
\centering
      \includegraphics[scale=0.25]{optim.pdf}
     \captionof{figure}{Impact of the reservation of the traffics.}   \label{fig:optimres}
  \end{minipage} 
     \begin{minipage}[b]{0.3\linewidth}
        \begin{center}
      \includegraphics[scale=0.55]{repart2}
            \vspace{0.5cm}
      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
      \end{center} 
  \end{minipage}
    \begin{minipage}[b]{0.30\linewidth}
        \begin{center}
      \includegraphics[scale=0.55]{repart1}
      \vspace{1cm}
      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
      \end{center} 
  \end{minipage}

  The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule. Indeed, our algorithm balanced the load of the C-RAN traffic over the period , that helps the BE traffic to not aggregate and create additional latency.
